---
title: "Project 3: STAT302package Tutorial"
author: "Tiffany Tian"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{STAT302package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of STAT302package is to demonstrate my learning on how to develop a well-documented, well- tested, and well-explained R package from the course of STAT 302. 

## Installation

You can install the STAT302package using the following line:

``` {r install, eval = FALSE}
devtools::install_github("txqtiffany/STAT302package", build_vignette = TRUE, build_opts = c())
```

and include a call to `library()` when using it.

## A tutorial for `my_t.test`

This is a basic example which shows you how to use `my_t.test`:

```{r my_t.test}
library(STAT302package)
```

## A tutorial for `my_lm`

This is a basic example which shows you how to use `my_lm`:

```{r my_lm}
library(STAT302package)
```

## A tutorial for `my_knn_cv`

This is a basic example which shows you how to use `my_knn_cv`:

```{r my_knn_cv}
library(STAT302package)
```

## A tutorial for `my_rf_cv`

This is a basic example which shows you how to use `my_rf_cv`:

```{r my_rf_cv}
library(STAT302package)
```
